%%%%%%
% Prathamesh Sonpatki - Resume
% Edited using Emacs 24
% Uses LaTeX and moderncv
% Forked from http://github.com/stultus
%%%%%%

\documentclass[11pt,a4paper]{moderncv}


% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[orange]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
% customizing link colors and formatting
\hypersetup{colorlinks=true}
%\hypersetup{a4paper=true}
\usepackage{color}
\definecolor{iorange}{RGB}{243,110,36}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Prathamesh}
\familyname{Sonpatki}
\title{Curriculum Vitae}
\address{B 12 Shriram Residency, Suvarnabaug Colony, Kothrud, Pune}{Maharashtra, India}
\mobile{+91-9422033142}
\email{csonpatki@gmail.com}
\usepackage{textcomp}
%\homepage {prathamesh-sonpatki.github.com}
\extrainfo{Blog: hey}
\extrainfo{IRC Nick: cha1tanya}
%\photo[54pt]{img.jpeg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

% --------------------------------------
% CONTENT
% --------------------------------------

\begin{document}
\maketitle

\section{Education}
\cvlistitem{Pursuing a Bachelors degree in \textit{Computer Science
    and Engineering} from Vishwakarma Institute Of Technology Pune.}

\section{Technical skills}
\cvcomputer
{\textbf{Operating Systems}}{Gnu/Linux
\\(Debian,Fedora,Ubuntu), \\Windows}
{\textbf{Programming Languages}}{ C, C++, Java, Ruby, HTML/CSS, JavaScript }
\cvcomputer
{\textbf{Development Tools}}{Emacs, Vim, Git, Bash, Netbeans}
{\textbf{Frameworks}}{ Ruby on Rails, JSP}
\cvcomputer
{\textbf{Software Packages}}{MySQL, PostgreSQL, LaTeX}
{}{}

% --------------------------------------
% WORK EX
% --------------------------------------

\section{Work Experience and Positions}

\cventry    
            {March 2012}
            {RubyConfIndia}
            {Volunteer}
            {}
            {}
            {
              Volunteer in RubyConfIndia 2012. \\ 
              RubyConfIndia is Indian edition of the international
              Ruby programming language conference. 
            }
\cventry
            {February 2012}
            {Melange 2012 Technical Events }
            {Co Ordinator}
            {VIT}
            {}
            {
             Co-Ordinated Cybernetics(CS/IT) Events in Technical Fest
             Melange.
            } 

\cventry
            {August 2011}
            {MiniDebConf Pune}
            {Organizer}
            {}
            {}
            {
             Organized MiniDebian Conference in VIT \\
             from 13th 2011 To 15th August 2011.    \\
             \url{http://wiki.debian.org/DebianIndia/MiniDebConf2011}, \\
             \url{http://is.gd/minidebconfpune}.
           }
\cventry
           {July 2011 -- present}
           {Diaspune}
           {Member}
           {}
           {}
           {
            Member of Diaspora Community , Helped in creating
            awareness about Diaspora. 
           }\\\\\\\\\\



%\subsection{Open Source Contributions}

%\cventry
 %        {}
  %       {Diaspora}
   %      {Contributor}
    %     {}
     %     {http://github.com/diaspora/diaspora/pull/2887} 
          
      %    {Sent a merge request for Diaspora -the distributed social
       %   networking website developed in Ruby on Rails. }


% --------------------------------------
% PROJECTS
% --------------------------------------


\section{Projects}

\cvlistitem
{\textbf
        {
         Job Scheduling in networked manufacturing using Game Theory
         and Genetic Algorithms
        }   
      \\A Java project to solve np-complete job scheduling problem \\
      in networked manufacturing using game theory and genetic algorithms.\\
      This is an ongoing project which has to be submitted as the 8th
      semester project(Major Project) \\
      Code - \url{http://github.com/prathamesh-sonpatki/JobScheduler}
}

\cvlistitem
{\textbf
      {CAthlon}  
      \\A Multiple Choice Questions app for programming competitions.\\
      Developed using JSP, HTML, CSS, MySql and Ruby.\\
      Used in Melange 2012 CAthlon (C Programming Event). \\
      Code - \url{http://github.com/prathamesh-sonpatki/CAthlon}
}


\cvlistitem
{\textbf{Online Judge} 
    Online Judge for programming competitions inspired from \url{http://spoj.pl} 
    and \url{http://codechef.com}\\
    Developed in JSP, HTML, CSS, MS Access. \\
    Submitted in 6th Semester (Minor Project). 
}




% --------------------------------------
% TALKS ETC.
% --------------------------------------

\section{Talks given and Workshops conducted}
\cventry
        {March 2012}
        {Introduction to Ruby}
        {VIT}
        {}
        {}
        {
         Presented an introductory talk on Ruby accompanied with a 
         hands-on workshop \\
         on basics of Ruby for about 35 College students.
         Presentation - \url{http://speakerdeck.com/u/chaitanya/p/introduction-to-ruby-vit-pune}
        }

% --------------------------------------
% CONFERENCES ATTENDED
% --------------------------------------
\section{Conferences Attended}

% --------------------------------------
% INTERESTS HOBBIES
% --------------------------------------
\cvlistitem
         {March 2012 - RubyConfIndia }
\cvlistitem
         {February 2012 - Gnunify }
\cvlistitem
         {November 2011 - Fudcon }
\cvlistitem
         {October 2011 - Fedora Activity Day At Red Hat Office Pune}
\cvlistitem
         {August 2011 - MiniDebConf }\\

\section{Interests and Hobbies}

\cvlistitem
           {An avid reader on technology,fiction and non-fiction books.\\}
\cvlistitem
           {
            Active member on problem solving and programing websites.\\
            Spoj Profile -          \url{http://spoj.pl/users/prathamesh43}   \\
            Codechef Profile -      \url{http://codechef.com/users/imchaitanya}\\
            Reliscore Profile -     \url{http://reliscore.com/user/chaitanya}
          }

  
% \cvlistitem{I watch a lot of movies and listen to Hindi and Malayalam film songs} 
% --------------------------------------

%---------------- Declaration-------------------
\section{Declaration}
\cvlistitem
            {
             I hereby declare that the information furnished 
             above is true to the best of 
             my knowledge and belief.\\ \\ \\
            }

\begin{minipage}{0.5\textwidth}
\begin{flushleft}
  \large
\bfseries Pune
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}

\begin{flushright}
  \large
\bfseries Prathamesh \textsc{Sonpatki}
\end{flushright}
\end{minipage}

%------------------------------------------


\end{document}
